SAYCAM preprocessing analyses from bounding box outputs

### 2021-12-21 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd
fix parentheses

      gold_sample_op_this_thres <- this_vid_data %>%
        filter(frame %in% frames_to_get$frame) %>%
        mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
        group_by(frame, vid_name, child_id) %>%
        summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>detection_thres) %>%
        mutate(detection_threshold = detection_thres)

@@

## Add in age data
all_gold_sample_frames_op <-all_gold_sample_frames_op %>%
  mutate(date_filmed = lubridate::ymd(str_split_fixed(vid_name,"_",4)[[2]])) %>%
  left_join(age_info) %>%
  rowwise() %>%
  mutate(age_days = as.numeric(difftime(date_filmed,bday)))

save(all_gold_sample_frames_op, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_from_bbs_2021_',dataset_type,'all_thresholds.RData')))

>>>>

      gold_sample_op_this_thres <- this_vid_data %>%
        filter(frame %in% frames_to_get$frame) %>%
        mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
        group_by(frame, vid_name, child_id) %>%
        summarize(hand_detected =sum(mean_confidence[label=='hand']>detection_thres),face_detected = sum(mean_confidence[label=='face']>detection_thres)) %>%
        mutate(detection_threshold = detection_thres)

@@

save(all_gold_sample_frames_op, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_from_bbs_2021_',dataset_type,'_all_thresholds.RData')))
